Verifying Demonstrations

### 2017-10-05 protocol.tex
Fixes typos in ProofFig

      \path[every node/.style={font=\small}]
      (manifesto) edge node [anchor=east] {$H(\cdot)$} (cid)
      (cid) edge node [anchor=east] {$PRF_{k_p}(\cdot)$} (pid)
      (pid) edge[bend right] node [anchor=north west] {$PRF_{k_w}(\cdot)$} (wid)
      % wsig
      (l) edge[bend right] (wsig)
      (ts) edge[bend right] (wsig)
      (wid) edge[bend right] node [anchor=north west] {$PRF_{k_w}(\cdot, \cdot, 
        \cdot)$} (wsig)
      ;

>>>>

      \path[every node/.style={font=\small}]
      (manifesto) edge node [anchor=east] {$H(\cdot)$} (cid)
      (cid) edge node [anchor=east] {$PRF_{k_P}(\cdot)$} (pid)
      (pid) edge[bend right] node [anchor=north west] {$PRF_{k_W}(\cdot)$} (wid)
      % wsig
      (l) edge[bend right] (wsig)
      (ts) edge[bend right] (wsig)
      (wid) edge[bend right] node [anchor=north west] {$PRF_{k_W}(\cdot, \cdot, 
        \cdot)$} (wsig)
      ;
